Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-12 paper.qmd
Updated Figure 12 title

```{r}
#| label: fig-one-dens_clust-error
#| fig-width: 15
#| fig-height: 10
#| fig-pos: H
#| out-height: 100%
#| fig-cap: "The sparse end of the structure shows a high model error, while the dense end shows a low model error. The tSNE layout of the C-shaped structure, with dense points (a) are colored according to their $4\\text{-}D$ error. Darker colors represent a high error, while lighter colors indicate a low error. b and c present the results from linked plots that brushed the high $4\\text{-}D$ error points in \\gD{} and $4\\text{-}D$. It helps in identifying the high $4\\text{-}D$ model errors that occur due to the sparse end. Videos of the linked plots are available at <>."

>>>>

```{r}
#| label: fig-one-dens_clust-error
#| fig-width: 15
#| fig-height: 10
#| fig-pos: H
#| out-height: 100%
#| fig-cap: "The sparse end of the structure shows a high model error, while the dense end shows a low model error. The tSNE layout of the C-shaped structure, with dense points (a1-a3) are colored according to their $4\\text{-}D$ model error. Darker colors represent a high error, while lighter colors indicate a low error. a2, a3 and b2, b3 present the results from linked plots that brushed the high $4\\text{-}D$ error points in \\gD{} and $4\\text{-}D$. It helps in identifying the high $4\\text{-}D$ model errors that occur due to the sparse end. Videos of the linked plots are available at <>."
